---
output: github_document
editor_options: 
  markdown: 
    wrap: 72
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# advancedmeancalculator

<!-- badges: start -->

<!-- badges: end -->

The goal of `advancedmeancalculator` package is to provide a simple and
flexible function `calculate_mean` for calculating the mean of numeric
vectors, with optional rounding capabilities. It handles NA values and
allows users to specify the number of decimal places for rounding.

## Installation

To use the `advancedmeancalculator` package, first install and load the
package `devtools`.

```{r}
#install and load devtools
install.packages("devtools")
library(devtools)
```

Next, install `advancedmeancalculator` from GitHub.

```{r}
install_github("stat545ubc-2024/assignment-b2-gnikas01")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# Load the package
library(advancedmeancalculator)

# Generate a numerical vector with an NA value
vector_NA <- c(1, 2, 3, NA, 5)

# Usage of calculate_mean function with a vector containing an NA value
example_result <- calculate_mean(vector_NA)
print(paste("Mean of vector_NA:", example_result))
```
